SIMD\slash SIMT-vectorized Sparse Chemical Kinetic Jacobian\slash Thermo-chemical Source-Term Evaluation

### 2018-06-01 paper.tex
reword

\Cref{F:source_parallel_scaling} shows the strong parallel scaling efficiency of source-term evaluation in \texttt{pyJac} on the \avx/ machine for both the shallow-vectorized Intel OpenCL and OpenMP codes.
In general, the \ce{H2}\slash\ce{CO} mechanism has the worst scaling efficiency for both Intel OpenCL and OpenMP, likely resulting from both its relatively small size, and few falloff\slash chemically activated reaction (in particular, the additional expensive logarithm and exponential evaluations that accompany them) \add{as demonstrated in~\cref{S:SIMD_scaling}}; i.e., there is simply not enough work to fully utilize the SIMD instructions\slash multiple threads.
Additionally, OpenMP tends to have higher scalings than the shallow-vectorized OpenCL code, e.g., \textasciitilde\num{0.9} and \textasciitilde\num{0.75} for \num{4} and \num{8} CPU cores, respectively, compared to just \numrange{0.66}{0.72} and \numrange{0.44}{0.48} for OpenCL; although not pictured (to keep the figure readable), the unvectorized Intel OpenCL code has only slightly worse scaling than the OpenMP code, hence the poorer scaling is unique to the shallow-vectorizated code.
This is due in large part to the superior performance of the shallow-vectorized OpenCL code, coupled with the relatively small amounts of work associated with source-term evaluation.
To illustrate this,~\cref{F:source_crossover} shows the mean run time per-condition of the OpenMP source-term evaluations for \numrange{2}{16} cores, compared to the shallow-vectorized OpenCL code on \num{1} (solid line) and \num{4} (dashed line) cores on the \avx/ machine.
For all chemical models, the mean run time per-condition (and hence the computational work allocated per-core, one of the key-drivers of parallel scaling efficiency~\cite{strong_scaling}) of OpenMP running on \num{4} cores is roughly equal to that of the shallow-vectorized OpenCL code on a single core.
Similarly, OpenMP running on \num{16} cores is roughly equivalent to the OpenCL code on \num{4} cores.
Therefore, a more fair comparison of parallel scaling efficiencies is to compare OpenCL running on \num{4} cores, to OpenMP on \num{16}; the OpenMP code's parallel efficiency drops to \textasciitilde\num{0.64} for \num{16} cores, similar to OpenCL's parallel scaling efficiency of \numrange{0.66}{0.72} at \num{4} cores.
Indeed, as will be seen in~\cref{S:jacobian_results} the strong parallel scaling efficiency for sparse Jacobian evaluation---the most computationally intensive task in this work---are far more similar between Intel OpenCL and OpenMP.

>>>>

\Cref{F:source_parallel_scaling} shows the strong parallel scaling efficiency of source-term evaluation in \texttt{pyJac} on the \avx/ machine for both the shallow-vectorized Intel OpenCL and OpenMP codes.
In general, the \ce{H2}\slash\ce{CO} mechanism has the worst scaling efficiency for both Intel OpenCL and OpenMP, likely resulting from both its relatively small size, and few falloff\slash chemically activated reaction (in particular, the additional expensive logarithm and exponential evaluations that accompany them); \add{as demonstrated in~\cref{S:SIMD_scaling} the amount of computational work required per thermo-chemical state plays a critical role in the full utilization of SIMD instructions\slash multiple threads}.
Additionally, OpenMP tends to have higher scalings than the shallow-vectorized OpenCL code, e.g., \textasciitilde\num{0.9} and \textasciitilde\num{0.75} for \num{4} and \num{8} CPU cores, respectively, compared to just \numrange{0.66}{0.72} and \numrange{0.44}{0.48} for OpenCL; although not pictured (to keep the figure readable), the unvectorized Intel OpenCL code has only slightly worse scaling than the OpenMP code, hence the poorer scaling is unique to the shallow-vectorizated code.
This is due in large part to the superior performance of the shallow-vectorized OpenCL code, coupled with the relatively small amounts of work associated with source-term evaluation.
To illustrate this,~\cref{F:source_crossover} shows the mean run time per-condition of the OpenMP source-term evaluations for \numrange{2}{16} cores, compared to the shallow-vectorized OpenCL code on \num{1} (solid line) and \num{4} (dashed line) cores on the \avx/ machine.
For all chemical models, the mean run time per-condition (and hence the computational work allocated per-core, one of the key-drivers of parallel scaling efficiency~\cite{strong_scaling}) of OpenMP running on \num{4} cores is roughly equal to that of the shallow-vectorized OpenCL code on a single core.
Similarly, OpenMP running on \num{16} cores is roughly equivalent to the OpenCL code on \num{4} cores.
Therefore, a more fair comparison of parallel scaling efficiencies is to compare OpenCL running on \num{4} cores, to OpenMP on \num{16}; the OpenMP code's parallel efficiency drops to \textasciitilde\num{0.64} for \num{16} cores, similar to OpenCL's parallel scaling efficiency of \numrange{0.66}{0.72} at \num{4} cores.
Indeed, as will be seen in~\cref{S:jacobian_results} the strong parallel scaling efficiency for sparse Jacobian evaluation---the most computationally intensive task in this work---are far more similar between Intel OpenCL and OpenMP.
